Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-10 extended_catalog/paper/extended_catalog.tex
better plots

% TODO:
%  how to format power-law, power-law, power law?

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Fermi Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that validate this tool.
We then calculate the Fermi LAT's sensitivity to spatially extended
sources.  We then use this tool to test all sources in the two
year source catalog for extension and report on the discovery
of XXXXXX\todo{What number should be put
here???} new extended sources.
\end{abstract}

@@

@@

\section{Extended Source Sensitivity}\label{extension_sensitivity}

We performed a second study to determine the LAT's sensitivity
to spatially extended sources. The sensitivity to extension
is defined as the flux at which the average value of
$\tsext$ is equal to $\langle\ts\rangle=25$. As was seen in
section~\ref{monte_carlo_validation}, this corresponds to an average
extension significance of $5\sigma$.
Qualitatively, we expect that the LAT would not be sensitive to
extended sources much smaller than the PSF. Similarly,
we expect that the LAT would not be sensitive to sources
much larger than the PSF since they would get lost in the
background.

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a uniform radially symmetric disk
morphology on top of a power-law Sreekumar-like isotropic spectrum
(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
over a one year time interval using a default rocking profile and a
livetime fraction of 0.8.  For a given extension and spectral index, we
first hand picked a flux range such that $\tsext<25$ and $\tsext>25$. We
then picked 10 flux points in this range and performed an extension test
for each of these fluxes. We repeated this procedure $>15$ times for each
spectral and spatial model.  By fitting a line to the flux vs $\tsext$,
we estimated when $\langle\tsext\rangle=25$.

Figure~\ref{index_sensitivity} shows the extension sensitivity for
sources of different spectral indices and extensions.  We selected
spectral indices 1.5, 2, 2.5, and 3 and 
extensions from $\sigma=0.1\deg$ to $2.0\deg$.  The curves
on the plot represent the division in extension and flux space where
$\langle\tsext=25\rangle$.  The plot shows by the sensitivity using all
photons with energy between 100 \mev and 100 \gev and the sensitivity
using only photons with energy between 1 \gev and 100 \gev.  This results
shows that the LAT's sensitivity to extension is better for harder sources
with more high energy photons. The sensitivity is best for sources with
an extension around $0.5\deg$ and is worse for small and large sources.

Except for the hardest and largest sources, our sensitivity is almost
unchanged when using events between 100 \mev and 1 \gev.  This is also
demonstrated in figure~\ref{ts_ext_vs_energy} which shows the \tsext for
the SNR IC443 in 12 energy bins between 100 \mev and 100 \gev. For IC443,
which has a spectral index ~2.4, almost the entire increase in \ts comes
from energies above 1 \gev.  On the other hand, other systematic errors
become increasingly important at low energy. For our extension search,
we include only photons above 1 \gev.

Figure~\ref{diff_factor_sensitivity} shows how the LAT's
sensitivity varies with increasing background, typical of sources
at lower galactic latitude. We compute the sensitivity for spectral
index 2 sources using 10 and 100 times the
extragalactic background. The latter result approximately represents the intensity of
the galactic diffuse emission near the galactic center. 
The figure shows two plots, the first showing the sensitivity looking only between 
1 \gev and 100 \gev and the second showing the sensitivity looking only
between 10 \gev and 100 \gev.
For each plot, the $y$ axis quotes the flux in the selected energy range
which weaken the dependence of the sensitivity on spectral index.
This shows that we are less sensitive to extended sources in
a higher background region and that if the flux is constant,
we are more sensitive if the source is harder (has more high energy
photons).

@@

The LAT two year catalog presented a search for all
statistically significant sources that are detected in the \gev
sky\cite{second_cat}.  The catalog group's source finding method assumes
that the emission originated as point sources and what was presented was
a list of all sources fit assuming a point source spatial hypothesis. 
Published extended sources were modeled by the catalog group as 
being extended, but no attempt was made to test if other sources in the catalog
could be spatially resolved.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

@@

\subsection{2FGL J1551.3-5333c}

% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
% Sources that had to be deleted
%   * P72Y2416 - 2FGL J1554.4-5317c
%   * P72Y2422 - Not a 2FGL source

The two year catalog source 2FGL J1551.3-5333c was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J1554.4-5317c which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source (\tsext=77.6) to the increase in log likelihood fitting
the region as two point sources (\tsinc=48.6).  Since the extended
hypothesis is a has a higher likelihood, we conclude that the source is
spatially extended More
information about the dual localization results for this source are
shown in table \ref{dual_localization_results}.

@@

% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% Deleted
%  *P72Y2490 - 2FGL J1520.6-5111c
%  *P72Y2487 - 2FGL J1619.7-5040c
%  *P72Y2496 - 2FGL J1622.8-5006
% Modify 
%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.410,-0.293,SkyDir.GALACTIC)

@@

\subsection{2FGL J2019.1+4040}

@@

% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
% Delete:
% * P72Y3287 - 2FGL J2021.5+4026
% * P72Y3262 - 2FGL J2013.8+4115c
% * P72Y3282 - 2FGL J2020.0+4159
% * P72Y3260 - 2FGL J2012.4+3955c
\todo[inline]{Describe how ROI was modified}

\todo[inline]{
Describe how this source is analyzed more carefully in the paper
``A cocoon of freshly accelerated cosmic rays detected by Fermi
in the Cygnus superbubble''}

@@

\subsection{2FGL J1834.7-0705c}

% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
% Delete:
% * P72Y2982 - Not a 2FGL source
% * P72Y2986 - 2FGL J1837.3-0700c
% * P72Y2994 - 2FGL J1839.3-0558c
% * P72Y2993 - 2FGL J1839.0-0539
% Modify:
% * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)
% * P72Y2974 - 2FGL J1834.7-0705c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)

@@

% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635

% Delete:
% * P72Y1291 - 2FGL J0853.5-4711
% * P72Y1296 - 2FGL J0855.4-4625
% * P72Y1274 - 2FGL J0848.5-4535
% * P72Y1259 - 2FGL J0842.9-4721
% * P72Y1310 - 2FGL J0901.7-4655
% * P72Y1300 - 2FGL J0858.0-4815
% Modify:
%  * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
%              (initial Position - SkyDir(265.5705,-0.0099)

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{This is the LAT's sensitivity to spatially
    extended sources. The $x$ axis is Monte Carlo extension of a
    simulated uniform disk source and the $y$ axis is the simulated
    source's 100 \mev to 100 \gev photon flux. Each curve represents
    the detection threshold for being able to spatially resolve an
    extended source (when $\langle\tsext\rangle=25$).  
    All sources have an assumed power-law spectrum and the different
    colors are for sources of different simulated spectral indices.
    The dashed line shows simulations using photons with energy between 
    100 \mev and 100 \gev while the solid lien shows simulations
    using photons with energy between 1 \gev and 100 \gev.
    The sensitivity is for a one year simulation against a Sreekumar-like
    isotropic background (\cite{sreekumar_isotropic}).
    This plot shows that our sensitivity is best for sources that are
    about $1\deg$ large. It also shows that for sources That are neither
    very large nor very soft, our sensitivity is not significantly
    improved using photons with energy between 100 \mev and 1 \gev.  More information
    about this plot is presented in section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
  % 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
  % N/A                - P72Y1287         - 2FGL J0851.7-4635

\clearpage
\begin{sidewaystable}
  \begin{centering}
    \begin{tabular}{r|rrrrrrrrrr}
      \hline
      \hline
      Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
      \hline
      \multicolumn{11}{c}{$E > 1\gev$} \\
      \hline
      2FGL J1627.0-2425c   &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
      2FGL J1551.3-5333c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
      2FGL J0823.0-4246    &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
      \hline
      \multicolumn{11}{c}{$E > 10\gev$} \\
      \hline
      2FGL J1615.2-5138          &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
      2FGL J1632.4-4753c         &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
      2FGL J2019.1+4040          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
      2FGL J1834.7-0705c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
      2FGL J0851.7-4635          &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
      \hline
    \end{tabular}
    \caption{The 8 new source candidates found by the
    extended source search. 3 new extended sources were found searching looking at photons with energies 1 \gev and
    5 new candidates were found looking at photons with energies above 10 \gev.
    The columns in this table have the same definition as table~\ref{known_extended_sources}.
    More information about these sources can be found in section~\ref{new_ext_srcs_section}
    }
    \label{new_ext_srcs_table}
  \end{centering}
\end{sidewaystable}

>>>>

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that validate this tool
and calculate the LAT's detection threshold to spatially extended
sources.  We then use this tool to test all sources in the two
year source catalog for extension and report on the discovery
of XXXXXX\todo{What number should be put
here???} new extended sources.
\end{abstract}

@@

\todo[inline]{Add note about how we had to delete nearby sources
which were not hard above 10GeV for analysis to converge.}

@@

\section{Extended Source Detection Threshold}\label{extension_sensitivity}

We performed a second study to determine the LAT's detection threshold
to spatially extended sources. The detection threshold to extension
is defined as the flux at which the average value of
$\tsext$ is equal to $\langle\ts\rangle=25$. As was seen in
section~\ref{monte_carlo_validation}, this corresponds to an average
extension significance of $5\sigma$.
Qualitatively, we expect that the LAT would not be sensitive to
extended sources much smaller than the PSF. Similarly,
we expect that the LAT would not be sensitive to sources
much larger than the PSF since they would get lost in the
background.

To calculate the LAT's detection threshold to spatially extended sources,
we simulated sources with a uniform radially symmetric disk
morphology on top of a power-law Sreekumar-like isotropic spectrum
(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
over a one year time interval using a default rocking profile and a
livetime fraction of 0.8.  For a given extension and spectral index, we
first hand picked a flux range such that $\tsext<25$ and $\tsext>25$. We
then picked 10 flux points in this range and performed an extension test
for each of these fluxes. We repeated this procedure $>15$ times for each
spectral and spatial model.  By fitting a line to the flux vs $\tsext$,
we estimated when $\langle\tsext\rangle=25$.

Figure~\ref{index_sensitivity} shows the threshold for
sources of different spectral indices and extensions.  We selected
spectral indices 1.5, 2, 2.5, and 3 and 
extensions from $\sigma=0.1\deg$ to $2.0\deg$.  The curves
on the plot represent the division in extension and flux space where
$\langle\tsext=25\rangle$.  The plot shows the threshold using all
photons with energy between 100 \mev and 100 \gev and the threshold
using only photons with energy between 1 \gev and 100 \gev.  This results
shows that the LAT's threshold to extension is better for harder sources
with more high energy photons. The threshold is best for sources with
an extension around $0.5\deg$ and is worse for small and large sources.

Except for the hardest and largest sources, our detection threshold is almost
unchanged when using events between 100 \mev and 1 \gev.  This is also
demonstrated in figure~\ref{ts_ext_vs_energy} which shows the \tsext for
the SNR IC443 in 12 energy bins between 100 \mev and 100 \gev. For IC443,
which has a spectral index ~2.4, almost the entire increase in \ts comes
from energies above 1 \gev.  On the other hand, other systematic errors
become increasingly important at low energy. For our extension search,
we include only photons above 1 \gev.

Figure~\ref{diff_factor_sensitivity} shows how the LAT's
detection threshold varies with increasing background, typical of sources
at lower galactic latitude. We compute it for spectral
index 2 sources using 10 and 100 times the
extragalactic background. The latter result approximately represents the intensity of
the galactic diffuse emission near the galactic center. 
The figure shows two plots, the first showing the threshold looking only between 
1 \gev and 100 \gev and the second showing the threshold looking only
between 10 \gev and 100 \gev.
For each plot, the $y$ axis quotes the flux in the selected energy range
which weaken the dependence of the detection threshold on spectral index.
This shows that we are less sensitive to extended sources in
a higher background region and that if the flux is constant,
we are more sensitive if the source is harder (has more high energy
photons).

@@

The LAT two year catalog presented a search for all
statistically significant sources that are detected in the \gev
sky (\cite{second_cat}).  The catalog group's source finding method assumes
that the emission originated as point sources and what was presented was
a list of all sources fit assuming a point source spatial hypothesis. 
Published extended sources were modeled by the catalog group as 
being extended, but no attempt was made to test if other sources in the catalog
could be spatially resolved.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

@@

\subsection{2FGL J1554.4-5317c}

% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% Sources that had to be deleted
%   * P72Y2416 - 2FGL J1551.3-5333c
%   * P72Y2422 - Not a 2FGL source

The two year catalog source 2FGL J1554.4-5317c was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
source 2FGL J1551.3-5333c
which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source (\tsext=77.6) to the increase in log likelihood fitting
the region as two point sources (\tsinc=48.6).  Since the extended
hypothesis is a has a higher likelihood, we conclude that the source is
spatially extended More
information about the dual localization results for this source are
shown in table \ref{dual_localization_results}.

@@

% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% Deleted
%  *P72Y2490 - 2FGL J1620.6-5111c
%  *P72Y2487 - 2FGL J1619.7-5040c
%  *P72Y2496 - 2FGL J1622.8-5006
% Modify 
%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.410,-0.293,SkyDir.GALACTIC)

@@

\subsection{2FGL J2021.5+4026}

@@

% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% Delete:
% * P72Y3282 - 2FGL J2019.1+4040
% * P72Y3287 - 2FGL J2020.0+4159
% * P72Y3262 - 2FGL J2013.8+4115c
% * P72Y3260 - 2FGL J2012.4+3955c
\todo[inline]{Describe how ROI was modified}

\todo[inline]{
Describe how this source is analyzed more carefully in the paper
\cite{A cocoon of freshly accelerated cosmic rays detected by Fermi
in the Cygnus superbubble}
}

@@

\subsection{2FGL J1837.3-0700c}

% 1FGL J1837.5-0659c - P72Y2986 - 2FGL J1837.3-0700c

% Delete:
% * P72Y2979 - 2FGL J1835.5-0649
% * P72Y2994 - 2FGL J1839.3-0558c
% * P72Y2993 - 2FGL J1839.0-0539

% Modify:
% * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)
% * P72Y2974 - 2FGL J1837.3-0700c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)

@@

% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
% Delete:
% * P72Y1291 - 2FGL J0853.5-4711
% * P72Y1296 - 2FGL J0855.4-4625
% * P72Y1274 - 2FGL J0848.5-4535
% * P72Y1259 - 2FGL J0842.9-4721
% * P72Y1310 - 2FGL J0901.7-4655
% * P72Y1300 - 2FGL J0858.0-4815
% Modify:
%  * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
%              (initial Position - SkyDir(265.5705,-0.0099)

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{This is the LAT's detection threshold to spatially
    extended sources. The $x$ axis is Monte Carlo extension of a
    simulated uniform disk source and the $y$ axis is the simulated
    source's 100 \mev to 100 \gev photon flux. Each curve represents
    the detection threshold for being able to spatially resolve an
    extended source (when $\langle\tsext\rangle=25$).  
    All sources have an assumed power-law spectrum and the different
    colors are for sources of different simulated spectral indices.
    The dashed line shows simulations using photons with energy between 
    100 \mev and 100 \gev while the solid lien shows simulations
    using photons with energy between 1 \gev and 100 \gev.
    The detection threshold is for a one year simulation against a Sreekumar-like
    isotropic background (\cite{sreekumar_isotropic}).
    This plot shows that our threshold is best for sources that are
    about $1\deg$ large. It also shows that for sources that are neither
    very large nor very soft, our sensitivity is not significantly
    improved using photons with energy between 100 \mev and 1 \gev.  More information
    about this plot is presented in section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
  % 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
  % N/A                - P72Y1287         - 2FGL J0851.7-4635

\clearpage
\begin{sidewaystable}
  \begin{centering}
    \begin{tabular}{r|rrrrrrrrrr}
      \hline
      \hline
      Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
      \hline
      \multicolumn{11}{c}{$E > 1\gev$} \\
      \hline
      2FGL J1627.0-2425c   &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
      2FGL J1554.4-5317c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
      2FGL J0823.0-4246    &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
      \hline
      \multicolumn{11}{c}{$E > 10\gev$} \\
      \hline
      2FGL J1615.2-5138          &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
      2FGL J1632.4-4753c         &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
      2FGL J2021.5+4026          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
      2FGL J1837.3-0700c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
      2FGL J0851.7-4635          &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
      \hline
    \end{tabular}
    \caption{The 8 new source candidates found by the
    extended source search. 3 new extended sources were found searching looking at photons with energies 1 \gev and
    5 new candidates were found looking at photons with energies above 10 \gev.
    The columns in this table have the same definition as table~\ref{known_extended_sources}.
    More information about these sources can be found in section~\ref{new_ext_srcs_section}
    }
    \label{new_ext_srcs_table}
  \end{centering}
\end{sidewaystable}

\clearpage
\begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{r|rr|rrrr|rrrr}
        \hline
        \hline
        Name                 &     \tsinc &     \tsext &      $\glon_1$ &      $\glat_1$ & $\text{Flux}_1$ ($10^{-9}$) &   $\text{Index}_1$ &      $\glon_2$ &      $\glat_2$ & $\text{Flux}_1$ ($10^{-9}$) &  $\text{Index}_2$ \\
        \hline
        \multicolumn{11}{c}{$E > 1\gev$} \\
        \hline
        2FGL J1627.0-2425c   &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
        2FGL J1554.4-5317c   &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
        2FGL J0823.0-4246    &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
        \hline
        \multicolumn{11}{c}{$E > 10\gev$} \\
        \hline
        2FGL J1615.2-5138    &       34.3 &       45.2 &     331.77\deg &      -0.35\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.5$  &     331.51\deg &      -0.83\deg & $       0.4 \pm        0.1$ & $  2.1 \pm   0.5$ \\
        2FGL J1632.4-4753c   &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
        2FGL J2021.5+4026    &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
        2FGL J1837.3-0700c   &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
        2FGL J0851.7-4635    &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
        \hline
      \end{tabular}
      \label{dual_localization_results}
      \caption{For the new extended source candidates in
      table~\ref{new_ext_srcs_table}, we describe the results
      of the dual localization procedure described in
      section~\ref{dual_localization_method}. Here, the extended
      source candidate is not fit as an extended source but instead
      fit as two point sources.  The dual localization is performed
      with \pointlike and results in the best fit position of the two
      sources $(\glon_1,\glat_1)$ and $(\glon_2,\glat_2)$.  The change
      in likelihood and spectral values are then computed using \gtlike
      with the best fit positions found by \pointlike.  \tsinc is the
      increase in TS fitting the region as two sources compared to
      fitting compared to fitting a single point source and is computed
      using \gtlike with the best fit positions taken from \pointlike.
      It can be directly compared to \tsext, which is taken from table~\ref{new_ext_srcs_table}.  For all of our candidates, $\tsext > \tsinc$
      which shows that an extended source fits the source better than two
      point sources.  As in table~\ref{known_extended_sources}, flux is
      measured in units of $10^{-9}\ph/\cm^2/\sec$ and is the integral
      flux between 1 \gev (10 \gev) and 100 \gev for the sources found
      using photons above 1 \gev (10 \gev).}
    \end{centering}
  \end{sidewaystable}

  \clearpage
  \begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{r|rrrrrrrr}
        \hline
        \hline
        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
        \hline
        \multicolumn{9}{c}{$E > 1\gev$} \\
        \hline
        2FGL J1627.0-2425c   &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
        2FGL J1554.4-5317c   &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
        2FGL J0823.0-4246    &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
        \hline
        \multicolumn{9}{c}{$E > 10\gev$} \\
        \hline
        2FGL J1615.2-5138    &                 74.7 &                 75.3 &                 88.7 &                     43.7 &                   45.2 &                 50.0 & $  0.52\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
        2FGL J1632.4-4753c   &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
        2FGL J2021.5+4026    &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
        2FGL J1837.3-0700c   &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
        2FGL J0851.7-4635    &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
        \hline
      \end{tabular}
      \label{alt_diff_model_results}
      \caption{
      This table shows a comparison of the \ts values gotten using \gtlike and \pointlike.
      It also compares the fit values using the standard diffuse model and using the alternate
      diffuse model described in section~\ref{alt_diff_model_description}.
      $\ts_\pointlike$ is the \ts of the source fit with the extended hypothesis using \pointlike
      whereas $\ts_\gtlike$ is the same quantity using the same model but fitting with \gtlike.
      There is very good agreement between the two methods.
      }
    \end{centering}
  \end{sidewaystable}
